\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2013-12-15 paper/paper.tex
Fixed a small error
Prefer <| over |> since <| is the same as the Haskell $ operator

Applying \texttt{extend} makes a \texttt{Signal Bool} wait a millisecond to
transition from true to false. Unlike a delay, true-to-false transitions still
occur immediately. By applying this function to every hovering Boolean in the
Menu structure, we give the mouse time to move from a menu Element to its
submenu before that submenu disappears. A millisecond was all that was needed.

A menu that does not detect mouse clicks is a fairly useless menu. There is no
primitive in Elm that can simply attach click detection to an element. To get
around this issue, we used a combination of \texttt{Mouse.clicks : Signal ()}
(which fires an event whenever the mouse clicks anywhere on the screen) and the
hoverable information to determine which element (if any) the mouse was hovering
over. (This implementation uses Elm's infix function application operator
\texttt{|>}, but it can be read as a pipeline.)

\begin{verbatim}
clicksFromHover : Signal Bool -> Signal ()
clicksFromHover hover =
    sampleOn Mouse.clicks hover
    |> keepIf id False
    |> lift (\_ -> ())
\end{verbatim}

>>>>

Applying \texttt{extend} makes a \texttt{Signal Bool} wait a millisecond to
transition from true to false. Unlike a delay, false-to-true transitions still
occur immediately. By applying this function to every hovering Boolean in the
Menu structure, we give the mouse time to move from a menu Element to its
submenu before that submenu disappears. A millisecond was all that was needed.

A menu that does not detect mouse clicks is a fairly useless menu. There is no
primitive in Elm that can simply attach click detection to an element. To get
around this issue, we used a combination of \texttt{Mouse.clicks : Signal ()}
(which fires an event whenever the mouse clicks anywhere on the screen) and the
hoverable information to determine which element (if any) the mouse was hovering
over. (This implementation uses Elm's infix function application operator
\texttt{<|}, which is the same as the Haskell operator \texttt{\$}.

\begin{verbatim}
clicksFromHover : Signal Bool -> Signal ()
clicksFromHover hover =
    lift (\_ -> ())
    <| keepIf id False
    <| sampleOn Mouse.clicks hover
\end{verbatim}
